Appendix 3: Example of a spatially varying effect of climate on citizen science count data with sdmTMB

### 2022-01-14 doc/appendix-pcod-sdmTMB.Rmd
Small appendix stuff

---
title: "Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
---

@@

For example, a mesh with a cutoff distance of 10 km can be made with

@@

We can inspect randomized quantile residuals:

```{r qqnorm, out.width="5in"}
pred$resid <- residuals(fit)
qqnorm(pred$resid)
qqline(pred$resid)
```

```{r plot-resids}
ggplot(pred, aes(X, Y, colour = resid)) +
  geom_point() +
  facet_wrap(~year) +
  coord_fixed() +
  scale_colour_gradient2()
```

@@

The above example used the default `bias_correct = FALSE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more detils can be found in the TMB documentation [https://github.com/kaskr/adcomp/wiki](https://github.com/kaskr/adcomp/wiki) or [Thorson & Kristensen (2016)](https://www.sciencedirect.com/science/article/abs/pii/S0165783615301399?via%3Dihub). Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements the generic by his correction algorithm that should correct for this, but can take considerable time and memory.

As an alternative, we can use the output from the joint precision matrix simulation draws to calculate our index. This should approximate the output of `get_index(x, bias_correct = TRUE)`. However, we note that there may be situations where this approach may fail or be biased.

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
saveRDS(ind, "sdmTMB-index-sim.rds")
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

>>>>

---
title: "Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
bibliography: refs.bib
csl: mee.csl
---

@@

For example, a mesh with a cutoff distance of 10 km can be made:

@@

We can inspect simulated residuals from the DHARMa package:

```{r sim-resids, out.width="3.5in", fig.align='center', warning=FALSE, results='hide'}
simulate(fit, nsim = 500) %>%
  dharma_residuals(fit)
```

@@

The above example used the default `bias_correct = FALSE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more detils can be found in the  [TMB documentation](https://github.com/kaskr/adcomp/wiki) or [@thorson2016bias]. Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements a generic bias correction algorithm that should correct for this, but can take considerable time and memory.

As an alternative, we can use the output from the joint precision matrix simulation draws to calculate our index. This should approximate the output of `get_index(x, bias_correct = TRUE)`. However, we note that there may be situations where this approach may fail or be biased and experimentation is ongoing.

```{r index-sims, out.width="5in"}
ind <- get_index_sims(pred_sims, area = rep(4, nrow(pred_sims)), level = 0.95)
ggplot(ind, aes(year, est / 1000)) +
  geom_line() +
  geom_ribbon(aes(ymin = lwr / 1000, ymax = upr / 1000), alpha = 0.4) +
  ylab("Biomass (t)")
```

# References

### 2022-01-14 doc/appendix-snow-sdmTMB.Rmd
Small appendix stuff

---
title: "Appendix 3: Example of a spatially varying effect of climate on citizen science count data with sdmTMB"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
urlcolor: blue
bibliography: refs.bib
---

>>>>

---
title: "Appendix 3: Example of a spatially varying effect of climate on citizen science count data with sdmTMB"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
urlcolor: blue
bibliography: refs.bib
csl: mee.csl
---
